\documentclass[11pt]{article}

\usepackage{sectsty}      % for section heading

\usepackage{libertine}    % font
\usepackage[T1]{fontenc}  % for 8-bit encoding
\renewcommand{\familydefault}{\sfdefault}

\usepackage{enumitem}     % for customizing itemize
\usepackage{hyperref}     % for link
\usepackage{mdwlist}      % for compact lists (itemize*)

\usepackage[letterpaper,margin=0.5in]{geometry}

\sectionfont{\normalfont\sectionrule{0pt}{0pt}{-4pt}{1pt}}

% format two pieces of text: one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
    #1 &
    #2 \\
\end{tabular*}}

\begin{document}
\thispagestyle{empty}

\begin{center}
    {\huge \textsc{\textbf{Rahul Venkatesh}}} \\[2pt]
    rahulv.9942@gmail.com
    $\mid$
    \href{https://www.linkedin.com/in/recurze}{linkedin.com/in/recurze}
    $\mid$
    \href{https://github.com/recurze}{github.com/recurze}
\end{center}

\section*{\textsc{\textbf{Education}}}
\begin{itemize}[leftmargin=0em]

\item[]
    \headerrow {\textbf{National University of Singapore (NUS)}}{Singapore}
    \headerrow {\emph{Master of Science in Data Science and Machine Learning}}{\emph{Aug 2023 -- Present}}

\item[]
    \headerrow {\textbf{Indian Institute of Technology (IIT), Delhi}}{New Delhi, India}
    \headerrow {\emph{Bachelor of Technology in Computer Science and Engineering}}{\emph{Jul 2016 -- Jun 2020}}

\end{itemize}

\section*{\textsc{\textbf{Technical Skills}}}
\begin{itemize}[itemsep=0em, leftmargin=0.7em]
\item[]
    \textbf{Languages}: Python, C++, SQL, Bash
\item[]
    \textbf{Libraries/Frameworks}: NumPy, Pandas, Scikit-learn, TensorFlow, Matplotlib, MongoDB
\end{itemize}

\section*{\textsc{\textbf{Work Experience}}}
\begin{itemize}[leftmargin=0em]
\parskip=0.1em

\item[]
    \headerrow {\textbf{Squarepoint Capital}}{Paris, France}
    \headerrow {\emph{Software Engineer}}{\emph{Aug 2020 -- Jun 2023}}

    \begin{itemize*}
        \item
            Developed and supported \textbf{low-latency} order entry gateways (OEG) for algorithmic trading in production.
        \item
            Built new OEGs to $5+$ \textbf{exchanges}, including \textbf{CME, ICE} and \textbf{OSE}
            over OUCH and FIX protocols.
        \item
            Designed frameworks for trading $2$ asset classes:
            \textbf{bonds} and \textbf{non-deliverable forwards (NDF)}.
        %\item
        %    \textbf{Improved performance} of gateway application by
        %    \textbf{collecting and analysing} latency-related \textbf{data}.
        %\item
        %    Coordinated with QA and delivered numerous projects (gateways) and business requests (features).
        %\item
        %    Documented workflows and automations to streamline developing new gateways and production support.
    \end{itemize*}
\end{itemize}

\section*{\textsc{\textbf{Projects}}}
\begin{itemize}[leftmargin=0em]

\item[]
    \headerrow {\textbf{Sentiment Analysis - Financial tweets}}{\href{https://github.com/recurze/fin_sentiment_analysis}{Source code}}
    \begin{itemize*}
        \item
            Preprocessed data by tokenizing, \textbf{stemming/lemmatizing} and vectorizing (\textbf{BoW and TF-IDF}) the text.
        \item
            Employed traditional ML models like Logistic Regression, SVM and \textbf{Naive Bayes} as baseline.
        \item
            Trained \textbf{LSTM} with both untrained and \textbf{pretrained embeddings} as an improvement over baseline.
        \item
            Tuned hyperparameters by randomized search and cross validation for robust and enhanced performance.
    \end{itemize*}

\item[]
    \headerrow {\textbf{Option Pricing}}{\href{https://github.com/recurze/OptionPricing}{Source code}}
    \begin{itemize*}
        %\item
        %    Developed n-step \textbf{Binomial Option Pricing Model} as a discrete version of Black-Scholes model.
        \item
            Implemented \textbf{Least-Square Policy Iteration} (RL) to learn optimal exercise policy for American options.
        \item
            Developed \textbf{Monte Carlo}, \textbf{tree models} and \textbf{PDE solvers} to price options like (quanto) European, Asian and DNT.
        %\item
        %    Applied LSTDQ to compute expected payoff upon continuation using Laguerre polynomials as \textbf{feature maps}.
        \item
            Solved convex optimization problem to build \textbf{arbitrage free smile} interpolator and implied \textbf{volatility surface}.
    \end{itemize*}

\item[]
    \headerrow {\textbf{Simple Stock Price Prediction}}{\href{https://github.com/recurze/StockPricePredictionNYSE}{Source code}}
    \begin{itemize*}
        \item
            Conducted time series analysis with \textbf{seasonal decomposition} and \textbf{stationarity} tests to identify patterns.
        \item
            Employed \textbf{Moving Average} and \textbf{Exponential Smoothing} to approximate prices and remove noise.
        %\item
        %    Implemented cross-validation and parameter grid search for model selection to reduce bias and overfitting.
        \item
            Used diverse forecasting methods, including \textbf{ARIMA} and \textbf{LSTM} (Recurrent Neural Network).
        \item
            Tested models against historical data to assess predictive performance and validate effectiveness.
    \end{itemize*}


\item[]
    \headerrow {\textbf{Numerical Solution to System of PDEs: Radiative Transfer (RT)}}{\href{http://github.com/recurze/SixDirScattering_RTESolver}{Source code}}
    \begin{itemize*}
        \item
            Solved system of PDEs modelling scattering in RT in 3D space in 6 directions for a range of $\sigma$
            (scattering coefficient).
        \item
            Designed stable numerical schemes for \textbf{Fixed-point} and \textbf{Symmetric Gauss-Seidel}
            (SGS) method with relaxation.
        \item
            Optimized SGS algorithm using matrix manipulation techniques for a 15x speed boost resulting in faster
            runtime.
    \end{itemize*}

%\item[]
%    \headerrow {\textbf{MiniMovieDB}}{}
%    \begin{itemize*}
%        \item
%            Developed a \textbf{MongoDB} database for managing and storing information about shows, actors and user events.
%        \item
%            Designed \textbf{aggregation pipelines} to extract valuable insights, such as identifying popular shows and actors.
%        \item
%            Enhanced query performance by strategic \textbf{indexing} and optimized regex searches for faster data retrieval.
%        \item
%            Implemented \textbf{FastAPI} endpoints to search, filter, and serve data seamlessly to the web frontend.
%    \end{itemize*}
%
\end{itemize}

%\section*{\textsc{\textbf{Relevant Coursework}}}
%\begin{itemize}[itemsep=0em, leftmargin=0.7em]
%\item[]
%    Probability and Stochastic Processes,
%    Differential Equations,
%    Optimization Algorithms for Data Modelling,
%    Machine Learning,
%    Applied Regression Analysis (In Progress),
%    Modelling and Numerical Simulations (In Progress),
%    Numerical Methods in Quantitative Finance (In Progress)
%\end{itemize}

\end{document}
